The population of long-period exoplanets --- \\ Fully-automated discovery \& characterization of long-period transiting exoplanet candidates in the \kepler\ archive \vspace{-3\baselineskip}

### 2016-06-30 document/ms.tex
stupid formatting
words about parameter estimation

\setlength{\voffset}{0in}
\setlength{\hoffset}{0in}
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{9in}
\setlength{\headheight}{0ex}
\setlength{\headsep}{\baselinestretch\baselineskip} % this is 2 lines in ``manuscript''
\setlength{\topmargin}{-\headsep}

@@

% Section spacing:
\makeatletter
\let\origsection\section
\renewcommand\section{\@ifstar{\starsection}{\nostarsection}}
\newcommand\nostarsection[1]{\sectionprelude\origsection{#1}}
\newcommand\starsection[1]{\sectionprelude\origsection*{#1}}
\newcommand\sectionprelude{\vspace{1em}}
\makeatother

@@

\newcounter{affilcounter}
\setcounter{affilcounter}{2}
\altaffiltext{1}{\url{danfm@uw.edu}; Sagan Fellow}

\edef \uw {\arabic{affilcounter}}\stepcounter{affilcounter}
\altaffiltext{\uw}       {Astronomy Department, University of Washington,
                          Seattle, WA, 98195, USA}

@@

For each transit candidate, we constrain the physical parameters of the system
by fitting the signal using a Keplerian orbit and a quadratic limb darkening
law for the central body.

>>>>

\setlength{\voffset}{0in}
\setlength{\hoffset}{0in}
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{9in}
\setlength{\headheight}{0ex}
\setlength{\headsep}{\baselinestretch\baselineskip} % this is 2 lines in ``manuscript''
\setlength{\footnotesep}{0in}
\setlength{\topmargin}{-\headsep}

@@

% Section spacing:
\makeatletter
\let\origsection\section
\renewcommand\section{\@ifstar{\starsection}{\nostarsection}}
\newcommand\nostarsection[1]{\sectionprelude\origsection{#1}}
\newcommand\starsection[1]{\sectionprelude\origsection*{#1}}
\newcommand\sectionprelude{\vspace{1em}}
\let\origsubsection\subsection
\renewcommand\subsection{\@ifstar{\starsubsection}{\nostarsubsection}}
\newcommand\nostarsubsection[1]{\subsectionprelude\origsubsection{#1}}
\newcommand\starsubsection[1]{\subsectionprelude\origsubsection*{#1}}
\newcommand\subsectionprelude{\vspace{1em}}
\makeatother

\widowpenalty=1000
\clubpenalty=1000

@@

\newcounter{affilcounter}
\altaffiltext{1}{\textsf{danfm@uw.edu}; Sagan Fellow}

\setcounter{affilcounter}{2}
\edef \uw {\arabic{affilcounter}}\stepcounter{affilcounter}
\altaffiltext{\uw}       {Astronomy Department, University of Washington,
                          Seattle, WA, 98195, USA}

@@

For each transit candidate, we constrain the physical parameters of the system
by fitting a section of light curve around each transit using an exposure time
integrated  Keplerian orbit with a quadratic limb darkening law for the
central body\footnote{Implemented at \url{https://github.com/dfm/transit};
this \paper\ uses git commit \textsf{482d99b} of that repository.}.
It has previously been established that the orbital period of a transiting
planet with only one transit can still be constrained given a measurement of
the stellar density and an assumption about the orbital eccentricity \cite[for
example][]{Wang:2015, Osborn:2016}.
Qualitatively this works because the transit of a bound body cannot have an
arbitrary period for a given duration.
This is the same argument used to justify the ``photoeccentric effect''
\citep{Dawson:2012} and the method of ``asterodensity profiling''
\citep{Kipping:2014b}.
In particular, this suggests that the periods of single transits in systems
with multiple inner planets will be especially well constrained
\citep{Kipping:2012}.
In this \paper, we do not take advantage of the extra constraints provided by
the inner planets, instead treating each long-period transiting system in
isolation, but this would be a good follow-up project.
